Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-17 CMSAC_presentation/josie_slides.qmd
updated with columns

::::: columns
::: {.column width="50%"}
```{r}
knitr::include_graphics("Mens-Basketball-Olympics-Getty-H-2024.jpeg")
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
knitr::include_graphics("jv_girls_basketball.png")
knitr::include_graphics("five_babies_playing_basketball.png")

@@

::: {.notes}
-   4 team single elimination tournament:
    -   Dream Team vs Work Group vs Middle School Girls Team vs Babies
-   If we only care about the top team winning, seeding structure does not matter
-   If we care about who gets second and third, seeding becomes important
    -   Would not pair up Work Group and Dream Team in the first round
:::

@@

```

>>>>

::: {.column width="50%"}
```{r}
knitr::include_graphics("Mens-Basketball-Olympics-Getty-H-2024.jpeg")
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
knitr::include_graphics("jv_girls_basketball.png")
knitr::include_graphics("five_babies_playing_basketball.png")

@@

::: notes
-   4 team single elimination tournament:
    -   Dream Team vs Work Group vs Middle School Girls Team vs Babies
-   If we only care about the top team winning, seeding structure does not matter
-   If we care about who gets second and third, seeding becomes important
    -   Would not pair up Work Group and Dream Team in the first round
:::

@@

```
::::::::::
